---
title: "Exam2_Taeyoung Lee"
author: "Taeyoung Lee"
date: "6/26/2020"
output: pdf_document
toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions

1. Please clear the environment in R.

```{r}
# clear the environment
rm(list=ls())

```


2. Load the “inequality” dataset into R, and save the data frame as ‘inequality_data’.

```{r}
# Load the dataset and save data frame
library(rio)
inequality_data = import("inequality.xlsx", which = 1)
```


3. Is this dataset a cross-sectional or panel dataset? Explain why in words and provide
some R code to prove that your answer is correct.

This data set is a cross-section dataset because it only has 2015 data.

```{r}
# See summary of year
summary(inequality_data$year)
```


4.The data frame contains a variable called inequality_gini. It corresponds to the
inequality Gini index, which “measures the extent to which the distribution of income
(or, in some cases, consumption expenditure) among individuals or households within
an economy deviates from a perfectly equal distribution.” In simple terms, there is a
lot of inequality when there are a lot of rich people and a lot of poor people but not a
lot of middle-class people. There is low inequality when most people are earning about
the same amount of income. Scandinavian countries like Sweden and Denmark tend
to have the most optimal Gini index scores. Using the subset command, provide the
inequality_gini scores for Denmark and Sweden.

```{r}
# Check the inequality score for Demark
subset(inequality_data, country=="Denmark")
```

```{r}
# Check the inequality score for Sweden
subset(inequality_data, country=="Sweden")
```


5. Since Brazil started the Bolsa Familia conditional cash transfer program in 1990s,
inequality in Brazil has decreased significantly. Just the same, inequality in Brazil is very
high comparatively. Using the subset command, please show the inequality_gini
score for Brazil.

```{r}
# Check the inequality score for Brazil
subset(inequality_data, country=="Brazil")
```


6. Given your answers to the previous questions, is it better to have a high or low
inequality_gini scores?

It is better to have a low inequality_gini score because Scandinavian countries like Sweden and Denmark that have low inequality show lower scores than Brazil.


7. Use the head command to get a quick peak at the data frame.

```{r}
# Take a quick peak
head(inequality_data)
```


8. Write a function called “accent.remove” to remove the accent on Belarus, apply that
function, and run the head command again to show that you removed the accent.

```{r}
# Remove accent for Belarus
accent.remove <- function(s)  {
  old1 <- "ú"
  new1 <- "u"
  s1 <- chartr(old1, new1, s)
}

# finish the accent FIX
inequality_data$country = accent.remove(inequality_data$country)

# Take a quick peak at the data
head(inequality_data)
```


9. Sort the data by the countries with the lowest inequality_gini scores and then run
the head command again to show what the top 5 countries are.

```{r}
# Sort the data 
inequality_data = inequality_data[order(inequality_data$inequality_gini),]

# Check the top 5 countries
head(inequality_data, n =5)
```


10. What is the mean inequality_gini score? Provide the relevant R code.

```{r}
# Check the mean
mean(inequality_data$inequality_gini, na.rm = TRUE)
```


11. Using the ifelse command, create two new dummy variables, high_inequality
and low_inequality, which takes values of either zero or one. The low_inequality
variable should correspond to countries with inequality_gini scores below the mean.
The high_inequality variable should correspond to countries with inequality_gini
scores above the mean. (Note: we will not accept answers that do not use the ifelse
command to create the variables.)

```{r}
# Creating dummy variables-- using ifelse
inequality_data$low_inequality = ifelse(inequality_data$inequality_gini < 36.81, yes = 1, no = 0 )
inequality_data$high_inequality = ifelse(inequality_data$inequality_gini > 36.81, yes = 1, no = 0 )

# Take a quick peak
head(inequality_data)
```


12. Run a cross-tab using the high_inequality and low_inequality variables that you created
in the previous question. The cross-tab should provide the mean inequality_gini
score and number of observations for each category of inequality. (Note: if you had
trouble using the ifelse command, we couldn’t provide points for the previous question.
However, you can create the variables using the indexing method)

```{r}
# Running a cross-tab
library(doBy)
summaryBy(high_inequality ~ low_inequality, data=inequality_data, FUN=c(mean,length))

```


13. The World Bank, the African Development Bank, and the Bill and Melinda Gates
Foundation are all working on reducing inequality in Africa. Write a for loop that
prints the names of these three actors. (Note: we will not accept answers that do not
provide a for loop.)

```{r}
# Create an organization vector
orgs <- c('World Bank', 'the African Development Bank', 'the Bill and Melinda Gates Foundation')

#create the for loop
for (i in orgs){
print (i)
}

```


14. Use this website to find a variable from the World Development Indicators that you
think is correlated with inequality. Tell us what variable you picked and why you picked
it. (Don’t worry if your prediction is not correct. We just want you to provide some
rationale.)

I think the variable "Income share held by highest 20%" will be highly correlated with inequality 
because the more income share the highest 20% hold, the higher inequlity score would be. 


15. Import that variable directly into R. (Note: if you are having trouble, read Mike Denly’s
Canvas announcement from the other day.)

```{r}
# add some data from the World Development Indicators (WDI)
remotes::install_github('vincentarelbundock/WDI')

# WDI package?
library(WDI)

head(WDI)

# Import the variable

income_data = WDI(country = "all",
    indicator = c("SI.DST.05TH.20"), # indicator from web
    start = 2015, end = 2015, extra = FALSE, cache = NULL)

```


16. Rename the variable that you imported into something that we can actually understand.

```{r}
# Rename variables
library(data.table)
setnames(income_data,"SI.DST.05TH.20", "income_share")

# Take a quick peak
head(income_data)
```


17. Merge the new variable into the other dataset, using inequality_data as the x and
and your new data frame as the y. When merging use the command that only keeps
the rows in your x data frame. Call your new data frame merged_df. Ensure that you
have no variables with .x or .y at the end of them in your new merged_df, while at
the same time ensuring there are still variables like country and year.

```{r}
# Merging data with a left-join
library(tidyverse)
merged_df = left_join(x=inequality_data,
                        y=income_data,
                        by =c("country", "year"))

# Check the variable names of new data frame
names(merged_df)

# Check if the country for iso2c.x and iso2c.y are matched
library(tidyverse)

merged_df<-
  merged_df %>%
  mutate(iso2c_match = ifelse(iso2c.x == iso2c.y,
                                  "yes",
                                  "no"))

# drop iso2c.x and rename iso2c.y
merged_df <-
  merged_df %>%
  select(-c("iso2c.x")) %>% 
  rename("iso2c" = "iso2c.y")
```


18. In merged_df, remove the missing data on the basis of inequality_gini and your
new variable that you took from the World Development Indicators.

```{r}
# Remove missing values
na.omit(merged_df, select=c("inequality_gini", "income_share"))

```


19. Using the filter command and piping method, only keep the data with
inequality_gini scores greater than 30. Save the new data frame as data_greater_30.
(Note: we will not accept answers using subset.)

```{r}
# Filter out thevariables
library(tidyverse) 
data_greater_30 <-
  merged_df %>%  # pipe(%>%): 
  dplyr::filter(!(inequality_gini <= 30))
```


20. Using data_greater_30, use to R to count how many countries have the sequence “ai”
in their name.

```{r}
grep("ai", data_greater_30)

```


21. Use any command from the apply family to take the sum of inequality_gini in
data_greater_30.

 
```{r}
sapply(data_greater_30$inequality_gini,sum)

```
 

22. Label your variables in merged_df. Any labels will suffice.

```{r}
#label the data
library(labelled)

# Drop countries match
merged_df$iso2c_match = NULL
 

var_label(merged_df) <- list(`country` = "Country",
                               `year` = "Year",
                               `inequality_gini` = "Inequality Gini Score",
                               `low_inequality` = "Inequality Gini Score < 36.81",
                               `high_inequality` = "Inequality Gini Score > 36.81",
                               `iso2c`= "ISO-2 Country Code")
                               
```

23. Save the labeled data frame as a Stata dataset called final_data.

```{r}
# Save the data frame as a Stata dataset
library(rio)
export(merged_df, "cleaned_dataset.dta")
```


24. Save all of the files (i.e. .Rmd, .dta, .xlsx, .pdf/Word Doc), push them to your
GitHub repo, and provide us with the link to that repo.

Git hup repo: https://github.com/taeyoung-lee/exam2



